---
title: "Main"
author: "Pablo Quesada Peyró"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
# Define the libraries that we're going to use
libraries <- c('pacman', 'tidyverse')

# Install them if not already installed
for (lib in libraries) {
  if (!require(lib, character.only = TRUE)) {
    install.packages(lib, dependencies = TRUE)
    library(lib, character.only = TRUE)
  }
}

# Load the libraries with pacman
pacman::p_load(tidyverse)
```

## What is all of this about?

The goal of this project is to show everybody whether if a person is working or not in Spain, depending on which province they're living in and what their gender are. It is important to know before taking this stats in account that the data shown is from 2002 and the firt quarter of 2024. The data is from [INE](https://www.ine.es/jaxiT3/Tabla.htm?t=65349) and it is public.


## Importing the data

To import the data we're going to use the library tidyverse. This library is a collection of packages that work together to make data manipulation easier. 

```{r}
# Import the data
data <- read.csv('data/tasa_ocupacion.csv', sep = ';', encoding = 'UTF-8')

# View the data
head(data)
```

The structure of the data is the following:
- 'Sexo' includes the sex of the person. It could be 'Mujeres', 'Hombres' or 'Ambos sexos'.
- 'Provincia' includes the code and the name of the province.
- 'Tasas' includes 'Tasa de actividad', 'Tasa de empleo de la población' and 'Tasa de paro de la población'.
- 'Periodo' includes the year and the quarter of the data.
- 'Total' includes the total of the data.


## Data cleaning


